---
title: "eventstudyr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{eventstudyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(eventstudyr)
```

## Event Studies

Linear panel models, and the “event-study plots” that often accompany them, are popular tools for learning about policy effects. 
 
## eventstudyr

`eventstudyr` facilitates running linear panel models and constructing "event-study plots" with the suggestions prescrbied in [Freyaldenhoven _et al._ (2021)](https://www.nber.org/system/files/working_papers/w29170/w29170.pdf). In particular, it provides functionality for:

* depicting cumulative estimated effects of a policy
* measuring the policy's effect relative to a user-controlled normalized period
* including the average value of the outcome corresponding to the normalized coefficient
* adding confidence intervals and sup-t confidence bands
* testing for the presence of "pre-trends" and dynamics leveling off
* plotting the least "wiggly" confound whose path is contained in the Wald region for the event-time path of the outcome. For more details, see the mathematical formulation and solution of the problem [here](https://github.com/JMSLab/EventStudyPackage/issues/7)
 
## Data
 
## `EventStudy()`
 
## `EventStudyPlot()`
